Our Title

### 2015-05-08 draft.tex
Added in many various edits, fixed commented areas of needed work.

@@

   \shortlipsum

@@

\subsection{Framework for how this report is formed}

\subsubsection{????? Missing ?????}

Missing

\subsection{Their potential targets (“declaratory policies”)}

@@

\section{What this report will focus on}

This  report will evaluate and discuss the ability of  ISIL to engage in nuclear terrorism, so as to inform a policy statement to be enforced by the U.S.. This report considers the capability and resources of other sovereign powers and terrorist organizations when those may benefit ISIL. This policy statement details an organized response to any step ISIL may make towards the deployment of a device containing special nuclear material (SNM). It stops short of a larger policy directed towards  the Administration's goal to degrade and ultimately destroy ISIL.

The scope of this  report is limited to the materials, signatures, and means of detection for those signatures, in all phases during the development and delivery of a nuclear device.

@@

\begin{itemize}
  \item The principle limitation is ISIL themselves and the broad lack of information and deep understanding of their goals and the methods they are willing to employ.
  \item The authors have no access to classified information and therefore are not privy to the most up-to-date information on current international strategies and capabilities of all parties involved in the following discussion and recommendations.
  \item As a whole, the authors have very limited experience in this field; this is not a complaint on the authors' part, but must be understood and accepted to understand the biases and limitations of this report.
  \item Per the definition of this assignment, the authors are limited in their analysis and discussion to the scenario of ISIL attempting to acquire WMD; post-acquisition will be touched on briefly but should be analyzed in depth in a future report and policy recommendation.
\end{itemize}

@@

\begin{itemize}
  \item The United States is interested in stopping ISIL from acquiring a nuclear weapon and willing to act decisively on this decision.
  \item ISIL does want to acquire WMD and will act decisively on this desire.
  \item All other assumptions are more specific and detailed and will be discussed in further depth throughout this report.
\end{itemize}

@@

\section{Scoping and problem - kind of summary and set framework for rest of report}

@@

As this is only a semester long project, there were great restraints on time and therefore scope. This report focuses solely on the paths to ISIL obtaining a nuclear capability. Of course, the fundamental way to preventing this would be to defeat ISIL in its entirety. However, given that the overall destruction of ISIL is a larger administration goal and is therefore being addressed by many other groups, our report focuses solely on nuclear capabilities. We also limited our scope by assuming that this policy applies only to the immediate future, and that if ISIL were to last for a longer time frame, more traditional state non-proliferation activities could take place.

@@

This section is meant to serve as a basic guide to technical concepts necessary for understanding nuclear weapons. Although the content has been distilled to the most fundamental information and is deliberately simplified, it is critical to understanding the scientific context that nuclear weapons find themselves in \cite{Prussin2014}.

@@

\subsection{???????  Needs content proofing   ????????}

@@

\subsection{??????  This makes some nods towards policy, and how to use the fuel cycle in our policy, but not much  ?????????}

@@

\section{Weapons  of interest}

@@

\subsection{???????? Scott's added brief RDD info, needs content proofing. Andrew tried to use it to link the above section to the case study below    ?????????}

@@

This list is subject to scrutiny and may be modified with further research.  For now, this serves as a snapshot of commercially or industrially available materials of the most interest in this evaluation.  Accounting for relative abundance and availability, the number of  isotopes of concern is reduced from ten to seven.  The remaining isotopes can be further categorized by type of radiation emissions:

@@

\begin{table}

@@

\subsubsection{?????? Scott's Brief Fusion Summary, needs  proofing}

A fusion device is a multistage weapon which consists of multiple fission stages and at least one fusion stage. The fission stages are used to drive the fusion reaction, which in turn provides a short, high energy pulse of neutrons which then drive additional fission. This complicated array of triggering devices is used in order to explosive yields which far exceed a single fission device. \autoref{fig:ulam_device} shows an example of a fusion device.

@@

Fusion weapons are far more sophisticated than fission weapons, and essentially consists of three fission devices and one fusion device. It is assumed that ISIL is pursuing nuclear weapons in order to commit acts of terrorism; optimizing yield does not greatly enhance the terror of a nuclear device. Due to the complexity of the design of multistage fusion devices, it is assumed that ISIL will elect to pursue gun-type fission weapons.

@@

\subsection{????? No substance for capabilities or much on current coalition efforts - Needs addressed.  Only need a little more in this section, but a more thorough overview of relevant capabilities should be in an appendix ?????}

@@

\subsection{????? I don't know what to do with this section.  It covers several area, makes unsubstantiated claims, and doesn't really coherently address the coalition or military capabilities.  I think this needs rewritten and focused.  Statements such as "the country [UK] is extra vulnerable to terrorist attacks on its nuclear installations" needs a reference and doesn't belong in this section (Perhaps an Appendix and a reference to that appendix in section 2.3.  Topic of discussion is bracketed ?????}

\subsection{????? From here... ?????}
The possibility of ISIL acquiring nuclear weapons means a stronger monitoring of nuclear-capable countries is needed. At the moment, only two handfuls of countries that have that capability.

UK and France have been U.S.' allies even since the country launched its global fight against terrorism after the 9/11 incident. Hence, the U.S. can expect UK specifically to be its closest ally in preventing ISIL's nuclear terrorism effort. The two countries \enquote{special relationship} dated back to Churchillian era means that the U.S. can usually count on the UK for mutual support, especially considering ISIL's threats to the country is very high. UK has been ISIL's main target for terrorist attacks, and given UK's nuclear capability, the country is extra vulnerable to terrorist attacks on any of its nuclear installations. So far, UK has joined U.S.-led coalition against ISIL, nevertheless, prospect for bilateral cooperation between the two countries cannot be disregarded.

Meanwhile, France is U.S.' oldest ally and relationship remains active and friendly. France supported U.S. in various issues, however, France was skeptical when U.S. invaded Iraq after the 9/11 incident. ISIL has also posed great threats to France (being a successful nuclear energy producer and all), France can be vulnerable to attacks on its nuclear energy facilities as well as its possession of nuclear weapons stocks. France is also among ISIL's main recruitments considering France high marginalized and discontented Muslim populations. France's high ISIL threats and vulnerabilities made the country a good collaborator in effectively fighting ISIL.

Nuclear capabilities in the hand of weak or unstable government give opportunity for ISIL to acquire nuclear capabilities. Nuclear capabilities of Pakistan and its weak governance as well as security vulnerabilities is of concern to the U.S.. Looking at U.S.-Pakistan relationship, it has its ups and down. Over the decades, Pakistan has been a great ally to the U.S., but there are a few instance where the two countries were in disagreement. U.S. viewed Pakistan as its ally and threat in the country's global war on terror, in which Pakistan is seen as the \enquote{weakest link} as it continue to fail in containing act of terrorism going on in its own country. U.S. need to prop Pakistan and reduce the country's vulnerabilities of ISIL penetrations and the possibility of ISIL acquiring Pakistan's nuclear weapons.

India is also another country with nuclear weapon capability, and is mostly on the \enquote{other side} of U.S.' security policies. India, together with Russia was among the pioneers of Non-Aligned Movement (NAM), in which views on security issues tend to be divergent with the U.S.. However, as of recently, the U.S. and India have set up \enquote{global strategic partnership}, based on shared democratic values and increasing convergence of interests on bilateral, regional and global issues; key recent developments in the relationship include the rapid growth of India's economy and bilateral trade, the close links between the Indian and American computer and Internet industries, a geopolitical coalition to balance the rise of China, the weakening of U.S.-Pakistan relations, among others. U.S. has cooperated with India in area of civil nuclear, and this can be expanded to development of nuclear security hopefully in the future. However, unlike Pakistan, India believed ISIL's threats as periphery issue to the country.

In analyzing Russia as a possible bilateral partner, the two country has had strained relationship, increasingly since the economic sanctions imposed by the U.S. to Russia. Dispute between the two countries have centered on power struggle for new world order, and recently exacerbated by Russia's annexation of Crimea. The two countries have been historical rival and the Cold War has proven to be one of the expansive and stretched out power struggle between the two. However, both countries realized and agreed to maintain dialogue in several areas including terrorism. Being misaligned with Russia on ISIL and nuclear terrorism issue could be serious mistakes as Russia's nuclear capability, if not protected and are allowed to be shared in the wrong hand, could have grave catastrophic impact to global security environment.

China, another U.S.' partner and rival at times, also have nuclear capabilities. China and the U.S. has close partnership particularly in economic sector, two-way trade between the two countries is over U.S.\$590 billion in 2014 alone. Chinese Muslim Uyghur militants have been associated with ISIL and efforts to undertake terrorist attacks in China. This strengthen the need for collaboration between China and U.S.; to ensure any ISIL activities can be contained in China and the country's nuclear weapons is protected from any probability of ISIL acquiring them.

U.S. considered North Korea as grave threats and this can be further exacerbated if North Korea is presented with the opportunity to work with ISIL. The prospect of North Korea selling their nuclear weapons and missiles to ISIL cannot be discounted. However, the possibility of U.S. and North Korea to cooperate in hampering this issue is not viable. The U.S. need to come up with initiatives to solve this problem.

Iran and U.S. shared a common enemy factor in terms of ISIL. As the nuclear talks between the two countries are being hashed out, both countries have committed on fighting ISIL together. This can be a good opportunity for U.S. to combat ISIL more effectively as U.S. cannot disregard Iran's influence and role in Iraq's security landscape and their fight against ISIL.
Meanwhile, collaborating with Israel is considered a gray area and not clear-cut as it seems. Israel has been known to voice their support of ISIL, keeping in line with ISIL's common enemy with Israel i.e. Iran. As U.S. and Israel have been a strong ally in the Middle East region, this fact presented a conundrum to the U.S..

The U.S. may find other allies in the Middle East region, however, the region is deeply divided in their positions against the ISIL. Although most Middle Eastern countries sees ISIL as a serious threat to the region and its people, some still supported ISIL, if not openly but explicitly. U.S. has worked closely with Jordan, with the U.S. creating a U.S.\$5 billion counterterrorism partnership fund with Jordan and other countries (Libya, Lebanon, Syria) that are considered on the \enquote{frontlines} of U.S.' fights against ISIL.

The U.S. can find allies in European countries as well, as the region is facing \enquote{recruitment} threats from ISIL. Thousands of Europeans have been recruited by ISIL to fight jihad cause in ISIL's territories. ISIL is also setting up bases in a number of European countries, expanding its influence beyond the Middle East region. The U.S. can identify these countries and create cooperation efforts in order to effectively eliminate ISIL.

\subsection{????? ...to here. ?????}

@@

\subsection{Timescale for data processing and response}

@@

\section{Etc...}

@@

These recommendations were developed by modeling the steps ISIL would have to take to procure a nuclear device, from the inception of the idea, to staging and detonation. Each recommendation is meant to target a specific chain of this logic model, with the ultimate goal of destroying all paths ISIL may have to a nuclear device. The logic model is shown in \autoref{fig:logic_tree}, with different nodes highlighted to represent the level of risk to the U.S., with green cells being high risk, orange medium, and red low.

@@

@@

Policy: Target ISIL Income Stream Proposed Policy: \textcolor{red}{Strengthen financial constraints and re-evaluate targeting}

\subsubsection{????????? Proposed Policy missing ??????????}

Proposed Policy: \textcolor{red}{???}

Lead Agency: Department of the Treasury

@@

Crippling ISIL oil revenue, however, is likely more complicated than it might seem. ISIL has been working to establish an internal market for their oil by providing cheap oil to the people in the territories they control, and by using it to fuel their own fleets \cite{Lister2014}. Some of the major U.S. airstrikes have targeted oil fields, but this also cuts off oil supplies for Syrian rebels and civilians in the region. This has been a central complaint of Syrian rebels, who lament that airstrikes disrupt oil supply to power generators and local facilities, allowing ISIL to pass the blame on to the United States. The United States should evaluate the viability of phasing away from targeting oil fields for strikes, and instead targeting ISIL's transportation and sale of oil. This approach may be made more viable by intelligence generated by DoT's efforts to identify everyone in the ISIL oil supply chain.

\subsubsection{?????? Need justification for the claim below ?????????}

In the meantime, the United States should provide large quantities of diesel fuel and oil for generators in opposition areas of northern Syria \cite{Lister2014}.

@@

\subsubsection{?????  What does this stand for ????????}

BAE systems and other surveillance and reconnaissance companies have mapped ISIL's social network by data mining to collect information from social media accounts linked to ISIL \cite{Tadjdeh2014}. These companies and others should be incentivized to continue to gather information on ISIL's efforts and to scour the Internet for threats, including identity and intellectual property theft. The State Department can support these efforts by providing incentives to the industry to provide the U.S. government with information about ISIL activities. A final recommendation is to put more of the government's own intelligence resources toward detecting ISIL social media fundraising efforts \cite{Report2015}.

@@

Lead Agency: National Security Agency

Contributing Agency: Intelligence Community and Department of State \normalfont

@@

\subsubsection{?????????  Policy missing ??????????}

Policy: \textcolor{red}{SUMMARY POLICY HERE}

\subsubsection{????????? Proposed Policy missing ??????????}

Proposed Policy: \textcolor{red}{SUMMARY POLICY HERE}

Airstrikes and other military interventions should be focused in areas that have oil reserves, mineral resources, ex-nuclear facilities, current nuclear facilities, and sources of electricity, heavy machining capabilities, and explosives production. We will present a series of maps to graphically display key areas where preventing and rolling back ISIL advances should be a priority.

@@

\chapter{???????  Add all ACRONYMS to table ?????}

>>>>

\usepackage{pdflscape}

@@

@@

\subsection{ISIL's potential targets (“declaratory policies”)}

@@

\section{Report Focus \& Framework}

This  report will evaluate and discuss the ability of  ISIL to engage in nuclear terrorism, so as to inform a policy statement to be enforced by the U.S.. This report considers the capability and resources of other sovereign powers and terrorist organizations when those may benefit ISIL. This policy statement details an organized response to any steps ISIL may make towards the deployment of a device containing special nuclear material (SNM). It stops short of a larger policy directed towards  the Administration's goal to degrade and ultimately destroy ISIL.

The scope of this  report is limited to the materials, signatures, and means of detection for those signatures, in all phases during the development and delivery of a nuclear device. A brief summary of the relevant material and technology involved in the production and detection of SNM and nuclear weapons is presented here, to provide the reader an understanding of the relevant material involved in formulating a response policy for this scenario. This information was used to model all potential pathways by which ISIL could obtain a nuclear weapon. Appropriate policies for breaking the links in this pathway were developed leveraging existing policies, and recommendations were proposed for eliminating the threat of a nuclear capable ISIL.

@@

\begin{itemize}
  \item The principle limitation is ISIL themselves and the broad lack of information and deep understanding of their goals and the methods they are willing to employ.
  \item The authors have no access to classified information and therefore are not privy to the most up-to-date information on current international strategies and capabilities of all parties involved in the following discussion and recommendations.
  \item As a whole, the authors have very limited experience in this field. This is not a complaint on the authors' part, but must be understood and accepted to understand the biases and limitations of this report.
  \item Per the definition of this assignment, the authors  limited  their analysis and discussion to the scenario of ISIL attempting to acquire WMD; post-acquisition will be touched on briefly but should be analyzed in depth in a future report and policy recommendation.
\end{itemize}

@@

\begin{itemize}
  \item The United States is interested in stopping ISIL from acquiring a nuclear weapon and is willing to act decisively on this decision.
  \item Due to the nature of this threat, it is assumed that the U.S. will initiate policies and measures to prevent ISIL acquisition of a nuclear weapon; international support will be leveraged as appropriate.
  \item ISIL does want to acquire WMD and will act decisively on this desire.
  \item It is assumed that this policy applies only to the immediate future, and that if ISIL were to last for a longer time frame, more traditional state non-proliferation activities could take place.
  \item All other assumptions are more specific and detailed and will be discussed in further depth throughout this report.
\end{itemize}

@@

\section{Problem Scoping}

@@

As this is only a semester long project, there were great restraints on time and therefore scope. This report focuses solely on the paths to ISIL obtaining a nuclear capability. Of course, the fundamental way to preventing this would be to defeat ISIL in its entirety. However, given that the overall destruction of ISIL is a larger administration goal and is therefore being addressed by many other groups, our report focuses solely on nuclear capabilities.

@@

This section is meant to serve as a basic guide to technical concepts necessary for understanding nuclear weapons. Although the content has been distilled to the most fundamental information and is deliberately simplified, it is critical to understanding the scientific context of nuclear weapons \cite{Prussin2014}. For flow of this report, the Nuclear Weapons Primer has been broken into 4 appendices:

\section{???????  Call out cross ref'd appendix names here ?????????}

@@

\section{??????? Move this section into its own appendix, following the glossary appendix ???????? }

Appendix XXXXXXX  covers the basic nuclear physics needed to understand the functioning of a a nuclear weapon. It covers topics such as nuclear structure, criticality, fission, fusion, and energy release, all of which are key to framing the development of a nuclear weapon. Additionally, it covers radioactive decay, radiation interactions with matter, and biological effects of radiation, useful for understanding the consequences of successful detonation of nuclear weapons or RDDs. These concepts and definitions will be used throughout the report to explain and formulate technical and policy solutions to eliminate pathways for ISIL acquisition of a nuclear weapon.

@@

\section{??????? Move this section into its own appendix, following the glossary appendix ???????? }

Appendix XXXXXXX  covers the basics of a nuclear fuel cycle necessary for both civilian and military uses of nuclear energy. The focus is on technologies and capabilities required to develop an indigenous nuclear weapons program. The Appendix addresses both the plutonium and uranium fuel cycles, and compares differences between the two. Any pathway to obtaining a nuclear weapon (other than theft or purchase of a complete nuclear weapon) will require one or more of the capabilities outlined in Appendix XXXXXXX.

@@

\section{Weapons of Interest}

\section{??????? Move this section into its own appendix, following the glossary appendix ???????? }

Appendix XXXXXXX  covers the basic categories of weapons enabled by nuclear materials: RDDs, fission weapons, and fusion weapons. This Appendix builds on the concepts outlined in

\section{??????? Cross ref to last two appendices ???????}

. Any ISIL pursuit of nuclear weapons or nuclear technology would ultimately result in the development of one of these three types of weapons.

@@

@@

This list is subject to scrutiny and may be modified with further research.  For now, this serves as a snapshot of commercially or industrially available materials of the most interest in this evaluation.  Accounting for relative abundance and availability, the number of  isotopes of concern is reduced from ten to seven.  The remaining isotopes can be further categorized by type of radiation emissions in \autoref{tab:decay_table_RDD}.

@@

\begin{table}[hb]

@@

A fusion device is a multistage weapon which consists of at least one fission stage and at least one fusion stage. The fission stages are used to drive the fusion reaction, which in turn provides a short, high energy pulse of neutrons which then drives additional fission. This complicated array of triggering devices is used in turn to achieve explosive yields which far exceed a single fission device. \autoref{fig:ulam_device} shows an example of a fusion device.

@@

Fusion weapons are far more sophisticated than fission weapons, and essentially consists of three fission devices and one fusion device. It is assumed that ISIL is pursuing nuclear weapons in order to commit acts of terrorism. While higher yields will result in larger damage,  optimizing yield does not necessarily enhance the terror factor of a nuclear device. Due to the complexity of the design of multistage fusion devices, it is assumed that ISIL will elect to pursue  fission weapons, most probably a gun-type design.

@@

@@

% 
% \subsection{????? I don't know what to do with this section.  It covers several area, makes unsubstantiated claims, and doesn't really coherently address the coalition or military capabilities.  I think this needs rewritten and focused.  Statements such as "the country [UK] is extra vulnerable to terrorist attacks on its nuclear installations" needs a reference and doesn't belong in this section (Perhaps an Appendix and a reference to that appendix in section 2.3.  Topic of discussion is bracketed ?????}
% 
% \subsection{????? From here... ?????}
% The possibility of ISIL acquiring nuclear weapons means a stronger monitoring of nuclear-capable countries is needed. At the moment, only two handfuls of countries that have that capability. 
% 
% UK and France have been U.S.' allies even since the country launched its global fight against terrorism after the 9/11 incident. Hence, the U.S. can expect UK specifically to be its closest ally in preventing ISIL's nuclear terrorism effort. The two countries \enquote{special relationship} dated back to Churchillian era means that the U.S. can usually count on the UK for mutual support, especially considering ISIL's threats to the country is very high. UK has been ISIL's main target for terrorist attacks, and given UK's nuclear capability, the country is extra vulnerable to terrorist attacks on any of its nuclear installations. So far, UK has joined U.S.-led coalition against ISIL, nevertheless, prospect for bilateral cooperation between the two countries cannot be disregarded.
% 
% Meanwhile, France is U.S.' oldest ally and relationship remains active and friendly. France supported U.S. in various issues, however, France was skeptical when U.S. invaded Iraq after the 9/11 incident. ISIL has also posed great threats to France (being a successful nuclear energy producer and all), France can be vulnerable to attacks on its nuclear energy facilities as well as its possession of nuclear weapons stocks. France is also among ISIL's main recruitments considering France high marginalized and discontented Muslim populations. France's high ISIL threats and vulnerabilities made the country a good collaborator in effectively fighting ISIL.
% 
% Nuclear capabilities in the hand of weak or unstable government give opportunity for ISIL to acquire nuclear capabilities. Nuclear capabilities of Pakistan and its weak governance as well as security vulnerabilities is of concern to the U.S.. Looking at U.S.-Pakistan relationship, it has its ups and down. Over the decades, Pakistan has been a great ally to the U.S., but there are a few instance where the two countries were in disagreement. U.S. viewed Pakistan as its ally and threat in the country's global war on terror, in which Pakistan is seen as the \enquote{weakest link} as it continue to fail in containing act of terrorism going on in its own country. U.S. need to prop Pakistan and reduce the country's vulnerabilities of ISIL penetrations and the possibility of ISIL acquiring Pakistan's nuclear weapons.
% 
% India is also another country with nuclear weapon capability, and is mostly on the \enquote{other side} of U.S.' security policies. India, together with Russia was among the pioneers of Non-Aligned Movement (NAM), in which views on security issues tend to be divergent with the U.S.. However, as of recently, the U.S. and India have set up \enquote{global strategic partnership}, based on shared democratic values and increasing convergence of interests on bilateral, regional and global issues; key recent developments in the relationship include the rapid growth of India's economy and bilateral trade, the close links between the Indian and American computer and Internet industries, a geopolitical coalition to balance the rise of China, the weakening of U.S.-Pakistan relations, among others. U.S. has cooperated with India in area of civil nuclear, and this can be expanded to development of nuclear security hopefully in the future. However, unlike Pakistan, India believed ISIL's threats as periphery issue to the country.
% 
% In analyzing Russia as a possible bilateral partner, the two country has had strained relationship, increasingly since the economic sanctions imposed by the U.S. to Russia. Dispute between the two countries have centered on power struggle for new world order, and recently exacerbated by Russia's annexation of Crimea. The two countries have been historical rival and the Cold War has proven to be one of the expansive and stretched out power struggle between the two. However, both countries realized and agreed to maintain dialogue in several areas including terrorism. Being misaligned with Russia on ISIL and nuclear terrorism issue could be serious mistakes as Russia's nuclear capability, if not protected and are allowed to be shared in the wrong hand, could have grave catastrophic impact to global security environment.
% 
% China, another U.S.' partner and rival at times, also have nuclear capabilities. China and the U.S. has close partnership particularly in economic sector, two-way trade between the two countries is over U.S.\$590 billion in 2014 alone. Chinese Muslim Uyghur militants have been associated with ISIL and efforts to undertake terrorist attacks in China. This strengthen the need for collaboration between China and U.S.; to ensure any ISIL activities can be contained in China and the country's nuclear weapons is protected from any probability of ISIL acquiring them.
% 
% U.S. considered North Korea as grave threats and this can be further exacerbated if North Korea is presented with the opportunity to work with ISIL. The prospect of North Korea selling their nuclear weapons and missiles to ISIL cannot be discounted. However, the possibility of U.S. and North Korea to cooperate in hampering this issue is not viable. The U.S. need to come up with initiatives to solve this problem.
% 
% Iran and U.S. shared a common enemy factor in terms of ISIL. As the nuclear talks between the two countries are being hashed out, both countries have committed on fighting ISIL together. This can be a good opportunity for U.S. to combat ISIL more effectively as U.S. cannot disregard Iran's influence and role in Iraq's security landscape and their fight against ISIL.
% Meanwhile, collaborating with Israel is considered a gray area and not clear-cut as it seems. Israel has been known to voice their support of ISIL, keeping in line with ISIL's common enemy with Israel i.e. Iran. As U.S. and Israel have been a strong ally in the Middle East region, this fact presented a conundrum to the U.S..
% 
% The U.S. may find other allies in the Middle East region, however, the region is deeply divided in their positions against the ISIL. Although most Middle Eastern countries sees ISIL as a serious threat to the region and its people, some still supported ISIL, if not openly but explicitly. U.S. has worked closely with Jordan, with the U.S. creating a U.S.\$5 billion counterterrorism partnership fund with Jordan and other countries (Libya, Lebanon, Syria) that are considered on the \enquote{frontlines} of U.S.' fights against ISIL.
% 
% The U.S. can find allies in European countries as well, as the region is facing \enquote{recruitment} threats from ISIL. Thousands of Europeans have been recruited by ISIL to fight jihad cause in ISIL's territories. ISIL is also setting up bases in a number of European countries, expanding its influence beyond the Middle East region. The U.S. can identify these countries and create cooperation efforts in order to effectively eliminate ISIL.
% 
% \subsection{????? ...to here. ?????}

@@

\subsection{Data Processing and Response Time}

@@

@@

These recommendations were developed by modeling the steps ISIL would have to take to procure a nuclear device, from the inception of the idea, to staging and detonation. Each recommendation is meant to target a specific chain of this logic model, with the ultimate goal of destroying all paths ISIL may have to a nuclear device. The logic model is shown in \autoref{fig:logic_tree}, with different nodes highlighted to represent the level of risk to the U.S., with green cells being high risk, orange medium, and red low. \autoref{fig:policy_chart} shows a summary of the existing and recommended policies, and are expanded upon in the sections to follow. In \autoref{fig:policy_chart}, the targeted capability and pathway coloring scheme corresponds to the same coloring scheme used in \autoref{fig:logic_tree}. The proposed policies are colored by their chance of success in disrupting the particular pathway: green is high, orange is medium, and red is low.

\subsection{????????  Update logic tree with Julie's new colored one ??????????}

@@

\begin{landscape}

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.55]{./figures/Policy_Chart2.png}
   \caption{Summary of existing and proposed policies to combat ISIL acquisition of nuclear weapons.}
     \label{fig:policy_chart}
\end{figure}

\end{landscape}

@@

Policy: \textcolor{red}{Target ISIL Income Stream Proposed Policy}

Proposed Policy: \textcolor{red}{Strengthen financial constraints and re-evaluate targeting}

Lead Agency: DoT

Contributing Agency: IC \normalfont

@@

Crippling ISIL oil revenue, however, is likely more complicated than it might seem. ISIL has been working to establish an internal market for their oil by providing cheap oil to the people in the territories they control, and by using it to fuel their own fleets \cite{Lister2014}. Some of the major U.S. airstrikes have targeted oil fields, but this also cuts off oil supplies for Syrian rebels and civilians in the region. This has been a central complaint of Syrian rebels, who lament that airstrikes disrupt oil supply to power generators and local facilities, allowing ISIL to pass the blame on to the United States. The United States should evaluate the viability of phasing away from targeting oil fields for strikes, and instead targeting ISIL's transportation and sale of oil. This approach may be made more viable by intelligence generated by DoT's efforts to identify everyone in the ISIL oil supply chain. In the meantime, the United States should provide large quantities of diesel fuel and oil for generators in opposition areas of northern Syria \cite{Lister2014}, in order to offset fuel and oil disruption due to U.S. targeting of oil fields. This would also diminish the demand for illegally-smuggled ISIL oil.

@@

British Aerospace (\enquote{BAE}) systems and other surveillance and reconnaissance companies have mapped ISIL's social network by data mining to collect information from social media accounts linked to ISIL \cite{Tadjdeh2014}. These companies and others should be incentivized to continue to gather information on ISIL's efforts and to scour the Internet for threats, including identity and intellectual property theft. The State Department can support these efforts by providing incentives to the industry to provide the U.S. government with information about ISIL activities. A final recommendation is to put more of the government's own intelligence resources toward detecting ISIL social media fundraising efforts \cite{Report2015}.

@@

Lead Agency: NSA

Contributing Agency: IC and DoS \normalfont

@@

Policy: \textcolor{red}{Targets of stretgic significance in support of allies}

Proposed Policy: \textcolor{red}{Target nuclear-capable infrastructure and resources}

Lead Agency: DoD

Contributing Agency: IC \normalfont

Airstrikes and other military interventions should be focused in areas that have oil reserves, mineral resources, ex-nuclear facilities, current nuclear facilities, and sources of electricity, heavy machining capabilities, and explosives production. We will present a series of maps to graphically display key areas where preventing and rolling back ISIL advances should be a priority. Although no specific targeting guidance as part of this policy, these maps highlight areas important for targeting purposes to prevent ISIL acquisition of a nuclear weapon.

@@

\chapter{???????  Add all ACRONYMS to table, reduce line spacing ?????}
